## rgbif use case - Ecological niche modelling (aka species distribution modelling)

```{r child="../knitopts.Rmd", include=FALSE}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width=7, 
  fig.height=6
)
```

In this example, we plot actual occurrence data for *Bradypus* species against a single predictor variable, BIO1 (annual mean temperature). This is only one step in a species distribution modelling nworkflow.

This example can be done using BISON data as well with our rbison package.

### Load libraries

```{r load, cache=FALSE}
library('rgbif')
library('dismo')
library('maptools')
library('plyr')
```

### Make a list of files that are installed with the dismo package, then create a rasterStack from these

```{r sdm1, cache=FALSE}
files <- list.files(paste(system.file(package="dismo"), '/ex', sep=''), 'grd', full.names=TRUE)
predictors <- stack(files)
```

### Get world boundaries.

```{r sdm2, cache=FALSE}
data(wrld_simpl)
```

### Get GBIF data using the rOpenSci package rgbif.

Lookup names

```{r sdm3, cache=FALSE}
namesdf <- name_lookup(query='bradypus*', rank="SPECIES", limit=60)$data
head(namesdf)
```

Get some name keys

```{r sdm4, cache=FALSE}
keys <- na.omit(unique(namesdf$nubKey))
```

Get occurrence data

```{r sdm5, cache=FALSE}
df <- occ_search(keys, hasCoordinate = TRUE, limit = 100, return = 'data')
df <- df[sapply(df, class) == "data.frame"]
df2 <- ldply(df)
df2 <- data.frame(lon=df2$decimalLongitude, lat=df2$decimalLatitude)
```

### Plot: (1) Add raster data, (2) Add political boundaries, (3) Add the points (occurrences)

```{r sdm6, cache=FALSE}
plot(predictors, 1)
plot(wrld_simpl, add=TRUE)
points(df2, col='blue')
```

### Further reading

The above example comes from [this tutorial][sdm] on species distribution modeling. 

[sdm]: http://cran.r-project.org/web/packages/dismo/vignettes/sdm.pdf
