## A more intuitive workflow

```{r}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
```

So there's a different way to work in R. It's all about pipes. Load `magrittr` and `dplyr`

```{r}
library('magrittr')
```

> %>% - pronounced "then" Pipe an object forward into a function call/expression.

```{r}
iris %>%
  head

iris %>%
  str
```

But more complicated as well

```{r}
library('dplyr')
library('magrittr')
```

```{r}
diamonds %>%
  group_by(color) %>%
  summarise(total = sum(price)) %>%
  arrange(desc(total)) %>%
  head(5)
```

Pretty intuitive, right?

------

We can use this with your workflow of getting data, manipulating, analysis, etc.

Here, we'll use the `rnoaa` package to search for stations around Athens, GA with `noaa_stations()`, pass those to `ncdc()`, then `filter()` and `arrange()` rows, then plot, and save the plot.

```{r}
library(rnoaa)
```

```{r eval=FALSE}
ids <- ncdc_stations(...)
ncdc('GHCND', stationid = ids, startdate = '2010-05-01', enddate = '2010-05-31') %>%
  filter(...) %>%
  arrange(...) %>%
  ggplot(aes(x, y)) + geom_line %>%
  ggsave("myplot.png")
```
