## taxize tries to make it easy to get identifiers from the various database sources

```{r}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
```


Here, get identifiers from 5 different sources for *Poa annua*. Then we can pass those ids to other functions that act on those ids without any other input

*p.s. this also demonstrates the interactive prompt, as you'll see*

```{r}
library('taxize')
out <- get_ids(names="Poa annua", db = c('ncbi','itis','col','tropicos'))
```

## Get a classification

### From ITIS

```{r}
classification(out$itis)
```

### From COL

```{r}
classification(out$col)
```

### From NCBI

```{r}
classification(out$ncbi)
```

## Get synonyms from Tropicos

```{r}
synonyms(out$itis)
```

## Many names - the ids class

In this case get many identifiers for many names, then pass in identifiers to get many classifications

```{r}
mynames <- c("Helianthus annuus","Pinus contorta","Collomia grandiflora")
out <- get_ids(names=mynames, db = c('ncbi','itis','col','tropicos'))
out$tropicos
class(out)
class(out$col)
classification(out$col)
```
