## Taxonomic hierarchy

```{r include=FALSE}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
```

### Hierarchies

A common task is getting the taxonomic tree upstream from your study taxa. We often know what family or order our taxa are in, but it we often don't know the tribes, subclasses, and superfamilies. taxize provides many avenues to getting classifications. Many are accessible via a single function (*classification*), including the Integrated Taxonomic Information System (ITIS) and National Center for Biotechnology Information (NCBI); and via the Catalogue of Life (see function *col_classification*):


Let's get classifications from ITIS using Taxonomic Serial Numbers. Note that we could use uBio instead.

```{r getdata}
library('taxize')
splist <- c("Helianthus annuus","Pinus contorta","Collomia grandiflora","Abies magnifica","Rosa californica","Datura wrightii","Mimulus bicolor","Nicotiana glauca","Madia sativa","Bartlettia scaposa")
class_list <- classification(splist, db="itis")
```

And we can attach these names to our allnames data.frame

```{r manipulate}
class_df <- cbind(class_list)
class_df$spname <- splist
```

Now that we have allnames_df, we can start to see some relationships among species simply by their shared taxonomic names

```{r index}
class_df[1:2,]
```

### downstream

We can also get downstream names, in this case all species from the genus *Apis*

```{r}
downstream("Apis", db="col", downto="Species")
```

Other searches:

* Get all genera in the rush family `downstream('Juncaceae', db='col', downto='Genus')`
* Get all phyla in the animal kingdom `downstream('Animalia', db='col', downto='Phylum')`

### Coming soon....

__UPSTREAM!__

```{r eval=FALSE, tidy=FALSE}
upstream ("Helianthus annuus", rank="genus")

$Helianthus annuus`
             name             rank
1            Helianthus       Genus
2            Iva              Genus
3            Achillea         Genus
4            ...etc         ...etc
```

