## Get common names from taxonomic names

```{r include=FALSE}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
```

You may want to collect taxonomic names for some reason in your research. taxize has a number of ways to do this. One is using `sci2comm` function

Define names

```{r definenames}
library('taxize')
splist <- c("Helianthus annuus","Pinus contorta","Collomia grandiflora","Abies magnifica","Rosa californica","Datura wrightii","Mimulus bicolor","Nicotiana glauca","Madia sativa","Bartlettia scaposa")
```

Search for common names

```{r search}
comnames <- sci2comm(splist, db="itis", simplify=TRUE)
```

Unfortunately, common names are not standardized like species names, so there are multiple common names for each taxon

```{r inspect}
sapply(comnames, length)
```

So let's just take the first common name for each species

```{r takefirst}
comnames_vec <- unname(sapply(comnames, function(x) x[[1]]))
```

And we can make a `data.frame` of our scientific and common names

```{r combine}
(allnames <- data.frame(spname = splist, comname = comnames_vec))
```
